Synpotic Soil Characterization

### 2025-02-21 3-reports/manuscript_figures.Rmd
add elevation and hyprop to rmd

>>>>

## Water retention curves

```{r gg_hyprop, fig.height=8, fig.width=10}
library(ggh4x)

tar_load(wrc_processed)

wrc_processed %>% 
  reorder_site() %>% 
    filter(kpa_fit >= 0 | kpa_eval >= 0) %>% 
    mutate(region = factor(region, levels = c("Erie", "Chesapeake"))) %>% 
    ggplot(aes(y = water_content_vol_percent, color = transect))+
    geom_line(aes(x = kpa_fit))+
    geom_point(aes(x = kpa_eval), shape = 1)+
    scale_x_log10(labels = scales::comma)+
  scale_color_manual(values = rev(soilpalettes::soil_palette("redox2", 3)))+
  labs(x = "Water potential, kPa",
       y = "Water content, % v/v",
       color = "")+
  #    facet_wrap(~region + site)+
  facet_nested_wrap(region ~ site)+
  theme_kp()
```

## Elevation

```{r, gg_elevation, fig.height=8, fig.width=10}

elevation = read.csv("synoptic-distances.csv", na = "")
elevation_processed = 
  elevation %>% 
  mutate(transect = factor(transect, levels = c("water edge", "wetland", "transition", "upland"))) %>% 
  reorder_site()

gg_wle = 
  elevation_processed %>% 
  filter(region == "Erie") %>% 
  ggplot(aes(x = distance_to_water_m, y = elev_m, color = transect))+
  geom_line(color = "black")+
  geom_point(size = 4)+
  scale_color_manual(values = c("grey", "#2E5894", "#FFB200", "#96001B"),
                     breaks = c("water edge", "wetland", "transition", "upland"))+
  facet_nested_wrap(region ~ site)+
  labs(x = "",
       y = "Elevation, m
       ",
       color = "")+
#  theme(legend.position = c(0.1,0.61))+
  NULL

gg_cb = 
  elevation_processed %>% 
  filter(region == "Chesapeake") %>%
  filter(site != "Sweet Hall Marsh") %>% 
  ggplot(aes(x = distance_to_water_m, y = elev_m, color = transect))+
  geom_line(color = "black")+
  geom_point(size = 4)+
  scale_color_manual(values = c("grey", "#2E5894", "#FFB200", "#96001B"),
                     breaks = c("water edge", "wetland", "transition", "upland"))+
  facet_nested_wrap(region ~ site)+
  labs(x = "Distance to water, m",
       y = "Elevation, m
       ",
       color = "")

ggpubr::ggarrange(gg_wle, gg_cb, common.legend = T, nrow = 2)
